Multispecies survey for diet comp

### 2020-12-01 SurveyDietCompTest.Rmd
outline bias steps WIP

sample_diet <- function(dat, fgs, alphamult = 10000000) {

@@

>>>>

sample_diet <- function(dat, fgs, unidprey = 0, alphamult = 10000000) {

@@

  # associate prey categories with unid categories
  fgs<- fgs%>% 
       mutate(unidtype = case_when((grouptype %in% c("mammal", "bird")) ~ "Unid_Vert",
                                   (grouptype %in% "fish") ~ "Unid_Fish",
                                   (grouptype %in% c("mammal")) ~ "Unid_Invert",
                                   (grouptype %in% c("lg_zoo", "med_zoo")) ~ "Unid_Plankton",
                                          TRUE ~ 0))

  # associate prey with prey category

  # add rows with unid categories

  # randomly assign up to unidprey % of prey in each prey category to associated unid category
